Douglas-complex fire smoke and cardiopulmonary morbidity

### 2017-11-03 r_scripts/analysis/oregon_cvd_pulm_results.Rmd
Cleaning up results code to be more streamlined.

**Note to Jingyang: I saw all the packages you used. How many do you actually need to run these analyses? It also looks like you need to run this markdown file on the server? I would like to avoid that and I can help you do this.**

Packages used:
```{r setup}
library(tidyverse)
```

>>>>

**Note to Jingyang 11/3/17: I saw all the packages you used. How many do you actually need to run these analyses? It also looks like you need to run this markdown file on the server? I would like to avoid that and I can help you do this.**

Packages used: tidyverse
```{r setup}
library(tidyverse)
```

##2. Wildfire smoke descriptive characteristics
Map of smoke count and smoke time series will go here.

##3. Descriptive table of number of health outcomes

Importing casecross over dataframes.
**Note to Jingyang 11/3/17: Same issue as above. How many of these files needs to be uploaded to produce results? A lot of this seems redundant or inefficient. I cannot find a lot of outcome files I need. I also need the SABA casecrossover dataframe. Listing example of two casecross over dataframes for now. Let's talk about this.**

```{r health data import}
# importing case-crossover dataframes 
# SABA case-crossover will be imported first
# i can't find a lot of the files
#resp_path <- paste0("./"

# asthma
asthma_path <- paste0("./data/health/2017-oregon_casecross_asthma.csv")
asthma_df <- read_csv(asthma_path)

# cvd 
cvd_path <- paste0("./data/health/2017-oregon_casecross_cvd.csv")
cvd_df <- read_csv(cvd_path)
# had a warning message for cvd dataframe import; should check on this

# import all other dataframes

# I think purrr would be a good way to loop through a list of outcome dataframes
# bind dataframes in a list
outcome_df_list <- list(asthma_df, cvd_df)
```

CVD warning message on import. Have Jingyang check. Maybe why proportion of CVD vs respiratory so different in Oregon?
*Warning message:In rbind(names(probs), probs_f) :number of columns of result is not a multiple of vector length (arg 1)*

Descriptive table will go here.

```{r descriptive table}
# name list elements
names(outcome_df_list) <- c( 'Asthma', 'CVD')

# output row of summary numbers
test_row <- asthma_df %>% 
  filter(outcome == 1) %>%
  group_by(age_ind) %>% 
  summarise(n = n()) %>%
  mutate(age_cat = ifelse(age_ind == 0, "age_under15",
                    ifelse(age_ind == 1, "age_15to65", "age_over65")))

  forcats::as_factor(age_ind, levels = c("age_under15", "age_15to65", "age_over65"))

glimpse(test_ro)

descriptive_table <- outcome_df_list %>% 
  lmap()

?lmap

mtcars %>%
  split(.$cyl) %>%
  map(~ lm(mpg ~ wt, data = .x)) %>%
  map(summary) %>%
  map_dbl("r.squared")

# Use map_lgl(), map_dbl(), etc to reduce to a vector.
# * list
mtcars %>% map(sum)
# * vector
mtcars %>% map_dbl(sum)
```

##4. Distributed lag cumulative effect results

##5. Distributed lag results

##6. Stratified cumulative results

##7. SABA cumulative effect by underlying respiratory diagnosis

### Comments:
1. File structure needs to be cleaned up. There are way too many subdirectories.
2. Remove r code files that are not useful. There are too many files with similar code inside.
3. Variables in the casecross over datasets raise some questions. For example, what is the difference from the varialbes geo_smk_pm and
